---
title: "Analysis of the mtcars Dataset"
author: "Sonisa Sharma"
date: "9.11.2019"
output:
  slidy_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  ioslides_presentation: default
runtime: shiny
---

## Coursera Reproducible Pitch

URL: *https://github.com/sonisa/Week4DevelopingDataProducts*


The mtcars dataset was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r}
library(datasets)
data("mtcars")
head(mtcars, 3)
```
## mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |
---

```{r server.R}

library(shiny)
shinyServer(function(input, output){
  mtcars$mpgsp <- ifelse(mtcars$mpg - 20 > 0, mtcars$mpg - 20, 0)
  model1 <- lm(hp ~ mpg, data = mtcars)
  model2 <- lm(hp ~ mpgsp + mpg, data = mtcars)
  
  model1pred <- reactive({
    mpgInput <- input$sliderMPG
    predict(model1, newdata = data.frame(mpg = mpgInput))
  })
  
  model2pred <- reactive({
    mpgInput <- input$sliderMPG
    predict(model2, newdata = 
              data.frame(mpg = mpgInput,
                         mpgsp = ifelse(mpgInput - 20 > 0,
                                        mpgInput - 20, 0)))
  })
  output$plot1 <- renderPlot({
  mpgInput <- input$sliderMPG
  
  plot(mtcars$mpg, mtcars$hp, xlab = "Miles Per Gallon", 
       ylab = "Horsepower", bty = "n", pch = 16,
       xlim = c(10, 35), ylim = c(50, 350))
  if(input$showModel1){
    abline(model1, col = "red", lwd = 2)
  }
  if(input$showModel2){
    model2lines <- predict(model2, newdata = data.frame(
      mpg = 10:35, mpgsp = ifelse(10:35 - 20 > 0, 10:35 - 20, 0)
    ))
    lines(10:35, model2lines, col = "blue", lwd = 2)
  }
  legend(25, 250, c("Model 1 Prediction", "Model 2 Prediction"), pch = 16, 
           col = c("red", "blue"), bty = "n", cex = 1.2)
  points(mpgInput, model1pred(), col = "red", pch = 16, cex = 2)
  points(mpgInput, model2pred(), col = "blue", pch = 16, cex = 2)
  })
  
  output$pred1 <- renderText({
    model1pred()
  })
  
  output$pred2 <- renderText({
    model2pred()
  })
  
})

shinyUI(fluidPage(
  titlePanel("Predict Horsepower from MPG"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("sliderMPG", "What is the MPG of the car?", 10, 35, value = 20),
      checkboxInput("showModel1", "Show/Hide Model 1", value = TRUE),
      checkboxInput("showModel2", "Show/Hide Model 2", value = TRUE),
      submitButton("Submit") # New!
    ),
    mainPanel(
      plotOutput("plot1"),
      h3("Predicted Horsepower from Model 1:"),
      textOutput("pred1"),
      h3("Predicted Horsepower from Model 2:"),
      textOutput("pred2")
      
    )
  )
))
```
---